Awareness and Experience of Developers to\\ Outdated and License-violating Code on Stack Overflow:\\ An Online Survey

### 2017-11-01 cloverflow_technical_report/cloverflow_survey_rn.tex
Improved the paper a little bit. Added some FIXMEs.

\title{Awareness and Experience of Developers to\\ Outdated and License-violating Code on Stack Overflow:\\ The Online Survey}
%\subtitle{Do you have a subtitle?\\ If so, write it here}

@@

\begin{abstract}
We performed two online surveys of Stack Overflow answerers and visitors to
assess their awareness to outdated code and software license in Stack Overflow
answerers. The answerer survey targets 607 highly reputable Stack Overflow users
and receives an impressive response rate of 33\%. Our findings are as follows.
Although most of the code snippets in the answers are written from scratch,
there are code snippets cloned from the questions, personal or company projects,
and from open source projects. Stack Overflow answerers are aware that some of
their snippets are outdated. However, 19\% of the participants report that they
rarely or never fix the code. At least 98\% of the answerers never include
software license in their snippets and 69\% never check for licensing conflicts
with Stack Overflow's CC BY-SA 3.0 if they copy the code from other sources to
Stack Overflow answers. The visitor survey uses convenient sampling and receives
89 responses. We found that 66\% of the participants experience a problem from
cloning and reusing Stack Overflow snippets. Fifty-six percent of the visitors
never report the problems back to Stack Overflow. Eighty-five percent of the
participants are not aware of CC BY-SA 3.0 license, and sixty-two percent never
give attributions to Stack Overflow posts or answers they copied the code from.
Moreover, 66\% of the participants do not check for licensing conflicts between
the copied Stack Overflow code and their software. With these findings, we
suggest Stack Overflow raise an awareness of their users, both the answerers and
the visitors, to the problem of outdated and license-violating code snippets.
\end{abstract}

@@

%This study is interested in the problem of outdated code and software licensing
%violations caused by code cloning on Internet-based question and answer
%websites.
Recent research shows that outdated third-party code and software licensing
conflicts are ramifications by code cloning, i.e.~reusing source code by copying
and pasting. \cite{Xia2014} report that a large number of open source systems
reuse outdated third-party libraries from popular open source projects. Using
the outdated code give detrimental effects to the software since they may
introduce vulnerabilities. On the other hand, \cite{German2009} found that code
cloning leads to conflicts in software license among different systems.

The Internet encourages fast and easy code cloning by sharing and copying the
code to and from online sources. Developers nowadays do not only clone code from
local software projects, but also from online sources such as programming Q\&A
website and online code
repositories~\citep{Acar2016,Abdalkareem2017,An2017,Yang2017}. Stack Overflow is
one of the most popular programming Q\&A websites in the world. It has 7.6
million users, 14 million questions, 23 million answers\footnote{Data as of 21
	August 2017 from~\url{https://stackexchange.com/sites}}, and more than 50
million developers visiting each month\footnote{Data as of 21 August 2017 from:
	\url{https://stackoverflow.com}}. Some code snippets on Stack Overflow are found
to be problematic. \cite{Acar2016} discovered that many code snippets provided
as solutions on Stack Overflow are workarounds and occasionally contains defects
or vulnerabilities. They performed a user study and found that although Stack
Overflow helps developers to solve Android programming problems quicker than
other resources, at the same time, offers less secure code than books or the
official Android documentation. Only 17\% of the Stack Overflow discussion
threads the participant visited during the study contain secure code snippets.
They also found a similar piece of an API call copied from Stack Overflow by
participants in their study occurring in a random sample of 200,000 Android apps
from Google Play. In addition, \cite{An2017} investigated clones between 399
Android apps and Stack Overflow posts. They found 1,226 code snippets which were
reused from 68 Android apps. They also observed that there are 1,279 cases of
potential license violations.

Asking and answering questions on Stack Overflow involves including source code
snippets, either in a question or an answer or both. While many answers contain
snippets that are written from scratch, there are several answers containing
code snippets copied from other sources. The copied snippets on Stack Overflow
is a snapshot of the code at the time of copying. They are less frequently
updated than in normal software projects and might not be up-to-date with their
originals, which are further modified due to bug fixing or feature improvements.
Besides, Some snippets are copied from software systems with stricter license
than Stack Overflow's Attribution-ShareAlike 3.0 Unported (CC BY-SA 3.0). Prior
to this study, we performed a quantitative empirical study using code clone
detection tools to locate cloned code snippets in accepted answers. We found
that many snippets were copied from open source projects. Some cloned snippets
are outdated (or obsolete) and some possibly violate the original software
license. These snippets are potentially harmful to reuse. To accompany the
findings and gain insights into the cause of the problems, we resort to a
qualitative study using an online survey of Stack Overflow developers who 1)
regularly answer programming questions with code snippets and 2) reuse code
snippets from Stack Overflow. \textbf{The study aims to understand the
	developers' awareness and experience to outdated code and code licensing on
	Stack Overflow.}

@@

\subsection{Survey Objective}
The main objective of the survey is to understand the developers' awareness and
experience to outdated code and code licensing on Stack Overflow. It can break
down into the following five research questions.

\begin{enumerate}
	\item \textbf{RQ1 (Sources of Stack Overflow Answer Snippets):} \textit{Where are the code snippets in Stack Overflow answers from?}
	\item \textbf{RQ2 (Awareness of Stack Overflow answerers to outdated code):} \textit{Are Stack Overflow answerers aware of outdated code in their answers?}
	\item \textbf{RQ3 (Awareness of Stack Overflow answerers to licensing conflicts):} \textit{Are Stack Overflow answerers aware of software licensing
		conflicts caused by code snippets in their answers?}
%	\item \textbf{RQ4 (Search for Coding Solutions):} \textit{Where do the developers search for programming solutions?}
	\item \textbf{RQ4 (Problems from Stack Overflow code snippets):} \textit{What are the problems Stack Overflow visitors experiencing from reusing code snippets on Stack Overflow?}
	\item \textbf{RQ5 (Software license of Stack Overflow code snippets):}\textit{Are Stack Overflow visitors aware of code licensing on Stack Overflow}
\end{enumerate}

@@

\subsection{Survey Design and Schedule}
The study is conducted using unsupervised online surveys. We designed the surveys using
Google Forms. We created two versions of the
survey: \textbf{the answerer survey}, and, \textbf{the visitor survey}. Both
surveys are completely anonymous and the participants could decide to leave at
any time. They do not collect any sensitive personal information from the
participants and are approved for an ethical waiver by the designated ethics
officer in the Computer Science Department at University College London (UCL). 
The complete version of the surveys can be found in 
Appendix~\ref{appendixA}.

\subsubsection{The answerer survey} 
The survey contains 11 questions: 7 Likert's
scale questions, 3 yes/no questions, and one open-ended question for additional
comments. The first two questions are mandatory while the other 9 questions will
be shown to the participants based on their previous answers. The survey
collects information about the participant's software development experience, the
experience of answering Stack Overflow questions, sources of the Stack Overflow
snippets, awareness of outdated code in their answers, concerns regarding
license when they copy code snippets to Stack Overflow, and additional
feedbacks. The survey was open for participation for 50 days, from 25 July 2017
to 12 September 2017, before we collected and analysed the responses.

\subsubsection{The visitor survey} 
The survey consists of 16 questions: 9 Likert's
scale questions, 3 yes/no questions, 2 multiple-choice questions, and 2
open-ended questions. The first four questions are mandatory while the other 12
questions will be shown to the participants based on their previous answers. The
survey collects information about the participant's software development
experience, the importance of Stack Overflow, reasons for reusing Stack Overflow
snippets, problems from Stack Overflow snippets, licensing of code on Stack
Overflow, and additional feedbacks. The survey was open for participation for 2 months, 
from 25 July 2017 to 25 September 2017, before we collected and analysed
the responses.

@@

\subsubsection{The answerer survey} 
We selected the participants for our answerer survey based on their Stack
Overflow reputations. On Stack Overflow, a user's reputation reflects how much
the community trusts the user. A user earns reputation when he or she receives
upvotes for good questions and useful answers. Accepted answers receive more
reputation score than questions and regular answers\footnote{Stack Overflow
	Reputation:~\url{https://stackoverflow.com/help/whats-reputation}}. Thus, Stack
Overflow reputation is an indicator of user's skills and their involvement in
asking and answering questions on the site.

@@

The participants were invited to take the survey via email addresses publicly
available on their Stack Overflow and GitHub profiles. We selected the answerers
based on their all-time reputation ranking\footnote{Stack Overflow Users (data as of
	25 July 2017):~\url{https://stackoverflow.com/users?tab=Reputation&filter=all}}
and separated them into two groups (see Table~\ref{tab:answerers}) so that we
can compare the results or observe similar patterns between them. The first
group had a reputation from 963,731 (the highest) to 7,674, and the second group
had a reputation from 7,636 to 6,999 which we sent out 300 and 307 emails
(excluding undelivered ones) respectively.

\subsubsection{The visitor survey} 
We adopted non-probability convenient sampling to invite participants for this
survey. Participation in the survey requires experience of visiting Stack
Overflow for solving programming tasks at least once. The participants were
invited to take the survey via five channels. The first channel is via the first
author's social media post (Facebook) inviting software developers who have
experience of copying code snippets from Stack Overflow to take the survey. The
second channel is a popular technology news and media community in Thailand
called \textsf{blognone.com} which attracts a high number of Thai software
developers. The first author posted an invitation to the visitor survey in a
discussion forum mentioning the requirements to take the survey. The third
channel collects answers from the University of Molise from the help of an
external researcher. The last two channels are from a
\textsf{comp.lang.java.programmer} Google groups and Software Engineering
Facebook page. The number of participants taken the survey is shown in
Table~\ref{tab:visitors}.

@@

\subsection{The answerer survey}
We received 117 answers (39\% response rate) from the first group and 84 answers
(27\% response rate) from the second group of Stack Overflow answerers. The response
rate from both groups was high considered other online survey in software
engineering that received approximately 14--20\%~\FIXME{double-check the
	citation again for the magic numbers.}~\citep{Punter2003}.

@@

The participants are active users and regularly answer questions on Stack
Overflow (see Figure~\ref{fig:survey_answer_frequency}). Eighty-two (82\%) and
sixty (61\%) of answerers from Group 1 and Group 2  answer questions at least
once a week. More than half of the answerers very frequently (81--100\% of the
time) or frequently (61--80\% of the time) include code snippets in their
answers. To break down into two groups as depicted in
Figure~\ref{fig:survey_answer_frequency_with_code}, Group 1 very frequently
(48.7\%) and frequently (27.4\%) provide code examples when answering. Likewise,
Group 2 follow the same trend (very frequently for 32.1\% and frequently for
36.9\%). Interestingly, there is one participant who never includes code snippet
in his/her answer thus the results after this question is from 116 participants.

@@

Half of the top answerers on Stack Overflow are aware of outdated code in their
answers. Seventy-one participants (61.2\%) of Stack Overflow answerers in Group
1 have been notified of outdated code in at least one of their answers. The
ratio drops to forty participants (47.1\%) in Group 2. We asked a follow up
question regarding the frequency of being notified of outdated code in their
answers. We found that only 0.5\% and 5.2\% of the answerers in Group 1
frequently or occasionally been notified. The answerers in Group 2 have very
frequently and occasionally been notified for 2.4\% and 3.5\% respectively.
Please note that we found inconsistencies between the answers of these two
questions. The percentage of participants who ``Never'' been notified of
outdated code in their Stack Overflow answers are 38.8\% and 52.9\% for Group 1
and Group 2 respectively. However, the answers for frequency of being notified
equal to ``Never'' decrease to 28.4\% and 43.5\% for Group 1 and 2 respectively
(see
Figure~\ref{fig:survey_outdated}~and~Figure~\ref{fig:survey_outdated_freq}).

@@

Regarding this issue of outdated code, one participant expresses their concern
in the open comment question: \textit{``The main problem for me/us is outdated
	code, esp. as old answers have high Google rank so that is what people see
	first, then try and fail. Thats why we're moving more and more of those examples
	to knowledge base and docs and rather link to those.''} On the other hand,
another participant does not  worry about his/her outdated code and how he
or she handles them: \textit{``On
	the matter of deprecation, I almost entirely use .NET which has got different
	versions of the framework. Therefore, code deprecation is not often a problem
	since what is deprecated on one version of the framework may be the only way of
	solving a given problem on an older version of the framework. I may also have to
	add that questions I tend to answer are about how to solve general coding
	problems so they are not usually subject to deprecation.''}

\vspace{0.5cm} \noindent\fbox{%
	\parbox[c][1cm]{0.98\textwidth}{%
		\textit{For RQ 2, Stack Overflow answerers are aware of outdated code in their
			answers. Nonetheless, there are approximately 19\% of the answerers who rarely
			or never fix their outdated code.} }%
}
\vspace{0.5cm}

@@

Almost every answerer in both groups, 114 out of 116 (98\%) and 84 out of 85
(99\%) respectively, does not include license statement in their code snippets
(numbers are shown in Figure~\ref{fig:survey_license}). Some of the participants
explain the reason in the open comment question which we summarised into three
groups as follows. First, they choose to post only their own code or code that
is adapted from the question. The code is automatically subjected to Stack
Overflow's CC BY-SA 3.0 without any explicit licensing statement. Second, they
copy the code from company or open source projects that they know are permitted
to be publicly distributed. Hence, no license statement is required. Third, some
answerers believe that code snippets in their answers are too small to claim any
intellectual property on them and fall under fair use~\citep{fairuse}.

@@

Since Stack Overflow is among the first research to solve programming tasks, we
ask the participants how frequently they reuse code snippets from answers on
Stack Overflow. According to the results (see
Figure~\ref{fig:survey_visitor_frequency_so_copy-crop}), we found that 57 (64\%)
participants actively reusing code snippets from Stack Overflow. Eight
participants (9\%) copy Stack Overflow code every day, 22 (25\%) do copying 3-6
times a week, 27 (30\%) do copying once or twice a week. There are 2
participants (2\%) who never copy the code from Stack Overflow.

@@

To sum up, Stack Overflow is ranked higher than official documentations, online
repositories, and book as the resource to look for programming solutions.
Developers rely on Stack Overflow answers because they are easy to search for on
the web. Moreover, 64\% of the participants reuse code snippets from Stack
Overflow at least once a week. The copy code from Stack Overflow because they
can be found easily from search engine, solve similar problems to their
problems, provide helpful context, and offer voting and accepted answers.

@@

We asked the visitors whether they have any problem from reusing Stack Overflow
code snippets and how often did the problems occur.  Fifty seven (out of eighty
seven) participants (see Figure~\ref{fig:survey_v_problems}) experienced a
problem from reusing Stack Overflow snippets. Among the 57, there are 2
participants who found problems in more than 80\% of the reused code snippets.
Eight and sixteen faced problems from at least sixty and forty percent of the
reused snippets.

@@

The problems from reusing Stack Overflow code snippets (illustrated in
Figure~\ref{fig:survey_visitor_problems}) include incorrect solutions, i.e.~the
code claims to solve the problem in the question while it does not,  (28 out of
57 $\approx$ 49\% participants reported this); outdated solutions, i.e.~the code
may work with the some older versions of the library or API, but not the one
they are using, (39 out of 57 $\approx$ 68\% participants reported this);
mismatched solutions, i.e.~the code solves the problem in the question but it is
not exactly the right solution for their problem, (40 out of 57 $\approx$ 70\%
participants reported this); and buggy code (1 out of 57 $\approx$ 2\%
participants reported this).

Stack Overflow visitors rarely report the problems back to the discussion
threads (as can be seen in
Figure~\ref{fig:survey_visitor_freq_report_problems}). Among the 32 participants
who encounter problems of Stack Overflow snippets, 18 of them (56\%) never
report the problems. Fourteen participants who reported the problems
did so by writing a comment (10), down-voting the answer (8), contacted the
answerer (2), and posting the new and correct answer (2), as shown in
Figure~\ref{fig:survey_visitor_how_report_problems}.

@@

\vspace{0.5cm} \noindent\fbox{%
	\parbox[c][2.2cm]{0.98\textwidth}{%
		\textit{For RQ4, our survey results show that 57 out of 87 Stack Overflow
			visitors find a problem from reusing Stack Overflow code snippets. Ten
			participants experience the problems from more than 80\% of the copied snippets and
			sixteen participants face the problems from 40--60\% of the reused code. The
			problems ranked by frequency include mismatched solutions (40), outdated
			solutions (39), incorrect solutions (28), and buggy code (1). Fifty-six percent
			of the participants never report the problems back to Stack Overflow.}}%
} \vspace{0.5cm}

@@

Fifty seven participants (66\%) never check for licensing conflicts at all
when reusing Stack Overflow code (see
Figure~\ref{fig:survey_visitor_licensing_conflict_check}). Lastly, possibly due
to their fairly small size of code which might fall under fair use, only 9\% of
the participants experience legal issues by reusing code snippets on Stack
Overflow (see Figure~\ref{fig:survey_visitor_legal_issue}). Nonetheless, as we designed the
survey to be anonymous, it is not possible to contact them for further details
on the legal issues they found.

@@

\vspace{0.5cm} \noindent\fbox{%
	\parbox[c][1.7cm]{0.98\textwidth}{%
		\textit{For RQ5, 85\% of the participants are not aware of Stack Overflow CC
			BY-SA 3.0 license and 62\% never give attributions to the Stack Overflow posts
			they copied the code snippets from. We found that 66\% of the visitors never check for software
	licensing conflicts between Stack Overflow code snippets and their projects.
	However, only 9\% of the participants encountered legal issues.}}%
} \vspace{0.5cm}

@@

\subsection{Internal Validity}
Due to a large number of users on Stack Overflow, we could invite only 607
developers to participate in the answerer survey. If all the developers are
invited, which is almost impossible considering 7.6 million users on Stack
Overflow, the results may be different. Nevertheless, we mitigate this threat to
internal validity by selecting the participants based on their Stack Overflow
reputation. This targeted participant selection ensures that we
invite developers who have been actively involved in asking and answering
questions on the site for a long period of time, and refrain from inviting new
users who merely answer a question or two. The highest reputation user invited
to our survey answered 33,933 questions and the lowest reputation user in our
survey answered 116 questions.

@@

From the answerer's responses, we discover that code in Stack Overflow answers
is usually written from scratch to answer a question. Nonetheless, there are
some code snippets that are copied from the answerer personal or company
projects, and open source software.

>>>>

\title{Awareness and Experience of Developers to\\ Outdated and License-violating Code on Stack Overflow:\\ An Online Survey}
%\subtitle{Do you have a subtitle?\\ If so, write it here}

@@

\FIXME{Should Rocco be added as an author?}

\FIXME{Check all occurrences of violating.}

\FIXME{Merge changes to the bib file from the TSE version.}

\begin{abstract}
We performed two online surveys of Stack Overflow answerers and visitors to
assess their awareness to outdated code and software licenses in Stack Overflow
answerers. The answerer survey targeted 607 highly reputed Stack Overflow users
and received a high response rate of 33\%. Our findings are as follows.
Although most of the code snippets in the answers are written from scratch,
there are code snippets cloned from the corresponding questions, from personal or company projects,
or from open source projects. Stack Overflow answerers are aware that some of
their snippets are outdated. However, 19\% of the participants report that they
rarely or never fix their outdated code. At least 98\% of the answerers never include
software licenses in their snippets and 69\% never check for licensing conflicts
with Stack Overflow's CC BY-SA 3.0 if they copy the code from other sources to
Stack Overflow answers. The visitor survey uses convenient sampling and received
89 responses. We found that 66\% of the participants experienced a problem from
cloning and reusing Stack Overflow snippets. Fifty-six percent of the visitors
never reported the problems back to the Stack Overflow post. Eighty-five percent of the
participants are not aware that StackOverflow applies the CC BY-SA 3.0 license, and sixty-two percent never
give attributions to Stack Overflow posts or answers they copied the code from.
Moreover, 66\% of the participants do not check for licensing conflicts between
the copied Stack Overflow code and their software. With these findings, we
suggest Stack Overflow raise awareness of their users, both answerers and
visitors, to the problem of outdated and license-violating code snippets.
\end{abstract}

@@

%This study is interested in the problem of outdated code and software licensing
%violations caused by code cloning on Internet-based question and answer
%websites.
Recent research shows that outdated third-party code and software licensing
conflicts are ramifications by code cloning, i.e.~reusing source code by copying
and pasting. \cite{Xia2014} report that a large number of open source systems
reuse outdated third-party libraries from popular open source projects. Using
the outdated code give detrimental effects to the software since they may
introduce vulnerabilities. On the other hand, \cite{German2009} found that code
cloning leads to software license conflicts among different systems.

The Internet encourages fast and easy code cloning by sharing and copying the
code to and from online sources. Developers nowadays do not only clone code from
local software projects, but also from online sources such as programming Q\&A
website and online code
repositories~\citep{Acar2016,Abdalkareem2017,An2017,Yang2017}. Stack Overflow is
one of the most popular programming Q\&A websites in the world. It has 7.6
million users, 14 million questions, 23 million answers\footnote{Data as of 21
	August 2017 from~\url{https://stackexchange.com/sites}}, and more than 50
million developers visiting each month\footnote{Data as of 21 August 2017 from:
	\url{https://stackoverflow.com}}. Some code snippets on Stack Overflow are found
to be problematic. \cite{Acar2016} discovered that many code snippets provided
as solutions on Stack Overflow are workarounds and occasionally contain defects
or vulnerabilities. They performed a user study and found that although Stack
Overflow helps developers to solve Android programming problems quicker than
other resources, at the same time, offers less secure code than books or the
official Android documentation. Only 17\% of the Stack Overflow discussion
threads the participant visited during the study contained secure code snippets.
They also found a similar piece of an API call copied from Stack Overflow by
participants in their study occurring in a random sample of 200,000 Android apps
from Google Play. In addition, \cite{An2017} investigated clones between 399
Android apps and Stack Overflow posts. They found 1,226 code snippets that were
reused from 68 Android apps. They also observed that there are 1,279 cases of
potential license violations.

Asking and answering questions on Stack Overflow involves including source code
snippets, either in a question or an answer or both. While many answers contain
snippets that are written from scratch, there are several answers containing
code snippets copied from other sources. The copied snippets on Stack Overflow
are snapshots of the code at the time of copying. They are less frequently
updated than in normal software projects and might not be up-to-date with their
originals, which are further modified due to bug fixing or feature improvements.
Besides, some snippets are copied from software systems with stricter licenses
than Stack Overflow's Attribution-ShareAlike 3.0 Unported (CC BY-SA 3.0). Prior
to this study, we performed a quantitative empirical study using code clone
detection tools to locate cloned code snippets in accepted answers. We found
that many snippets were copied from open source projects. Some cloned snippets
are outdated (or obsolete) and some possibly violate the original software
license. These snippets are potentially harmful to reuse. To accompany the
findings and gain insights into the cause of the problems, we resort to a
qualitative study using an online survey of Stack Overflow developers who 1)
regularly answer programming questions with code snippets and 2) reuse code
snippets from Stack Overflow. \textbf{The study aims to understand the
	developers' awareness and experience to outdated code and code licensing on
	Stack Overflow.}

@@

\subsection{Survey Objective}
The main objective of the survey is to understand the developers' awareness and
experience to outdated code and code licensing on Stack Overflow. It addresses
the following five research questions.

\begin{enumerate}
	\item \textbf{RQ1 (Sources of Stack Overflow Answer Snippets):} \textit{Where are the code snippets in Stack Overflow answers from?}
	\item \textbf{RQ2 (Awareness of Stack Overflow answerers to outdated code):} \textit{Are Stack Overflow answerers aware of outdated code in their answers?}
	\item \textbf{RQ3 (Awareness of Stack Overflow answerers to licensing conflicts):} \textit{Are Stack Overflow answerers aware of software licensing
		conflicts caused by code snippets in their answers?}
%	\item \textbf{RQ4 (Search for Coding Solutions):} \textit{Where do the developers search for programming solutions?}
	\item \textbf{RQ4 (Problems from Stack Overflow code snippets):} \textit{What are the problems Stack Overflow visitors experiencing from reusing code snippets on Stack Overflow?}
	\item \textbf{RQ5 (Software license of Stack Overflow code
            snippets):} \textit{Are Stack Overflow visitors aware of code licensing on Stack Overflow?}
\end{enumerate}

@@

\subsection{Survey Design and Schedule}
The study is conducted using unsupervised online surveys. We designed the surveys using
Google Forms. We created two versions of the
survey: \textbf{the answerer survey} and \textbf{the visitor survey}. Both
surveys are completely anonymous and the participants could decide to leave at
any time. They do not collect any sensitive personal information from the
participants and are approved for an ethical waiver by the designated ethics
officer in the Computer Science Department at University College London (UCL). 
The complete version of the surveys can be found in 
Appendix~\ref{appendixA}.

\subsubsection{The answerer survey} 
The survey contains 11 questions: 7 Likert's
scale questions, 3 yes/no questions, and one open-ended question for additional
comments. The first two questions are mandatory while the other 9 questions will
be shown to the participants based on their previous answers. The survey
collects information about the participant's software development experience, the
experience of answering Stack Overflow questions, sources of the Stack Overflow
snippets, awareness of outdated code in their answers, concerns regarding
license when they copy code snippets to Stack Overflow, and additional
feedback. The survey was open for participation for 50 days, from 25 July 2017
to 12 September 2017, before we collected and analysed the responses.

\subsubsection{The visitor survey} 
The survey consists of 16 questions: 9 Likert's
scale questions, 3 yes/no questions, 2 multiple-choice questions, and 2
open-ended questions. The first four questions are mandatory while the other 12
questions will be shown to the participants based on their previous answers. The
survey collects information about the participant's software development
experience, the importance of Stack Overflow, reasons for reusing Stack Overflow
snippets, problems from Stack Overflow snippets, licensing of code on Stack
Overflow, and additional feedback. The survey was open for participation for 2 months, 
from 25 July 2017 to 25 September 2017, before we collected and analysed
the responses.

@@

\subsubsection{The answerer survey} 
We selected the participants for our answerer survey based on their Stack
Overflow reputations. On Stack Overflow, a user's reputation reflects how much
the community trusts the user. A user earns reputation when he or she receives
upvotes for good questions and useful answers. \FIXME{I don't
  understand the sentence:} Accepted answers receive more
reputation score than questions and regular answers\footnote{Stack Overflow
	Reputation:~\url{https://stackoverflow.com/help/whats-reputation}}. Thus, Stack
Overflow reputation is an indicator of user's skills and their involvement in
asking and answering questions on the site.

@@

The participants were invited to take the survey via email addresses publicly
available on their Stack Overflow and GitHub profiles. We selected the answerers
based on their all-time reputation ranking\footnote{Stack Overflow Users (data as of
	25 July 2017):~\url{https://stackoverflow.com/users?tab=Reputation&filter=all}}
and separated them into two groups (see Table~\ref{tab:answerers}) so that we
can compare the results or observe similar patterns between them. The first
group had a reputation from 963,731 (the highest) to 7,674, and the second group
had a reputation from 7,636 to 6,999. We sent out 300 and 307 emails
(excluding undelivered ones) to the two groups respectively.

\subsubsection{The visitor survey} 
We adopted non-probability convenient sampling to invite participants for this
survey. Participation in the survey requires experience of visiting Stack
Overflow for solving programming tasks at least once. The participants were
invited to take the survey via five channels. The first channel is via the first
author's social media post (Facebook) inviting software developers who have
experience of copying code snippets from Stack Overflow to take the survey. The
second channel is a popular technology news and media community in Thailand
called \textsf{blognone.com} which attracts a high number of Thai software
developers. The first author posted an invitation to the visitor survey in a
discussion forum mentioning the requirements to take the survey. The third
channel collected answers from the University of Molise with the help of an
external researcher. The last two channels are the
\textsf{comp.lang.java.programmer} group and the Software Engineering
Facebook page. The number of participants taken the survey is shown in
Table~\ref{tab:visitors}.

@@

\subsection{The answerer survey}
We received 117 answers (39\% response rate) from the first group and 84 answers
(27\% response rate) from the second group of Stack Overflow answerers. The response
rate from both groups was high considering other online surveys in software
engineering~\citep{Punter2003}.

@@

The participants are active users and regularly answer questions on Stack
Overflow (see Figure~\ref{fig:survey_answer_frequency}). Eighty-two (82\%) and
sixty (61\%) of answerers from Group 1 and Group 2  answer questions at least
once a week. More than half of the answerers very frequently (81--100\% of the
time) or frequently (61--80\% of the time) include code snippets in their
answers. To break down into two groups as depicted in
Figure~\ref{fig:survey_answer_frequency_with_code}, Group 1 very frequently
(48.7\%) and frequently (27.4\%) provide code examples when answering. Likewise,
Group 2 follow the same trend (very frequently for 32.1\% and frequently for
36.9\%). Interestingly, there is one participant in the first group who never includes code snippet
in his/her answer thus the results after this question is from 116
participants of the first group.

@@

Half of the top answerers on Stack Overflow are aware of outdated code in their
answers. Seventy-one participants (61.2\%) of Stack Overflow answerers in Group
1 have been notified of outdated code in at least one of their answers. The
ratio drops to forty participants (47.1\%) in Group 2. We asked a follow up
question regarding the frequency of being notified of outdated code in their
answers. We found that only 0.5\% and 5.2\% of the answerers in Group 1
are frequently or occasionally been notified. The answerers in Group 2 have very
frequently and occasionally been notified for 2.4\% and 3.5\% respectively.
Please note that we found inconsistencies between the answers of these two
questions. The percentage of participants who have ``Never'' been notified of
outdated code in their Stack Overflow answers are 38.8\% and 52.9\% for Group 1
and Group 2 respectively. However, the answers for the frequency of being notified
equal to ``Never'' decrease to 28.4\% and 43.5\% for Group 1 and 2 respectively
(see
Figure~\ref{fig:survey_outdated}~and~Figure~\ref{fig:survey_outdated_freq}).

@@

Regarding the issue of outdated code, one participant expresses their concern
in the open comment question: \textit{``The main problem for me/us is outdated
	code, esp. as old answers have high Google rank so that is what people see
	first, then try and fail. Thats why we're moving more and more of those examples
	to knowledge base and docs and rather link to those.''} On the other hand,
another participant does not  worry about his/her outdated code and how he
or she handles them: \textit{``On
	the matter of deprecation, I almost entirely use .NET which has got different
	versions of the framework. Therefore, code deprecation is not often a problem
	since what is deprecated on one version of the framework may be the only way of
	solving a given problem on an older version of the framework. I may also have to
	add that questions I tend to answer are about how to solve general coding
	problems so they are not usually subject to deprecation.''}

\vspace{0.5cm} \noindent\fbox{%
	\parbox[c][1cm]{0.98\textwidth}{%
		\textit{For RQ 2, Stack Overflow answerers are aware of outdated code in their
			answers. Nonetheless, there are approximately 19\% of the answerers who rarely
			or never fix their outdated code for which
                        they have been notified.} }%
}
\vspace{0.5cm}

@@

Almost every answerer in both groups, 114 out of 116 (98\%) and 84 out of 85
(99\%) respectively, do not include license statement in their code snippets
(numbers are shown in Figure~\ref{fig:survey_license}). Some of the participants
explain the reason in the open comment question which we summarised into three
groups as follows. First, they choose to post only their own code or code that
is adapted from the question. The code is automatically subjected to Stack
Overflow's CC BY-SA 3.0 without any explicit licensing statement. Second, they
copy the code from company or open source projects that they know are permitted
to be publicly distributed. Hence, no license statement is required. Third, some
answerers believe that code snippets in their answers are too small to claim any
intellectual property on them and fall under fair use~\citep{fairuse}.

@@

Since Stack Overflow is among the first research to solve programming tasks, we
asked the participants how frequently they reuse code snippets from answers on
Stack Overflow. According to the results (see
Figure~\ref{fig:survey_visitor_frequency_so_copy-crop}), we found that 57 (64\%)
participants actively reusing code snippets from Stack Overflow. Eight
participants (9\%) copy Stack Overflow code every day, 22 (25\%) do copying 3-6
times a week, 27 (30\%) do copying once or twice a week. There are 2
participants (2\%) who never copy code from Stack Overflow.

@@

To sum up, Stack Overflow is ranked higher than official documentation, online
repositories, and books as the resource to look for programming solutions.
Developers rely on Stack Overflow answers because they are easy to search for on
the web. Moreover, 64\% of the participants reuse code snippets from Stack
Overflow at least once a week. The copy code from Stack Overflow because they
can be found easily from search engine, solve similar problems to their
problems, provide helpful context, and offer voting and accepted answers.

@@

We asked the visitors whether they have had any problem from reusing Stack Overflow
code snippets and how often did the problems occur.  Fifty seven (out of eighty
seven) participants (see Figure~\ref{fig:survey_v_problems}) experienced a
problem from reusing Stack Overflow snippets. Among the 57, there are 2
participants who found problems in more than 80\% of the reused code snippets.
Eight and sixteen faced problems from at least sixty and forty percent of the
reused snippets.

@@

The problems from reusing Stack Overflow code snippets (illustrated in
Figure~\ref{fig:survey_visitor_problems}) include incorrect solutions, i.e.~the
code claims to solve the problem in the question while it does not  (28 out of
57 $\approx$ 49\% participants reported this); outdated solutions, i.e.~the code
may work with the some older versions of the library or API, but not the one
they are using (39 out of 57 $\approx$ 68\% participants reported this);
mismatched solutions, i.e.~the code solves the problem in the question but it is
not exactly the right solution for their problem (40 out of 57 $\approx$ 70\%
participants reported this); and buggy code (1 out of 57 $\approx$ 2\%
participants reported this).

Stack Overflow visitors rarely report the problems back to the discussion
threads (as can be seen in
Figure~\ref{fig:survey_visitor_freq_report_problems}). Among the 32 participants
who encounter problems of Stack Overflow snippets, 18 of them (56\%) never
report the problems. Fourteen participants who reported the problems
did so by writing a comment (10), down-voting the answer (8), contacted the
answerer (2), and posting the new and correct answer (2) (shown in
Figure~\ref{fig:survey_visitor_how_report_problems}).

@@

\vspace{0.5cm} \noindent\fbox{%
	\parbox[c][2.2cm]{0.98\textwidth}{%
		\textit{For RQ4, our survey results show that 57 out of 87 Stack Overflow
			visitors encountered a problem from reusing Stack Overflow code snippets. Ten
			participants experienced problems for more than 80\% of the copied snippets and
			sixteen participants faced problems for 40--60\% of the reused code. The
			problems ranked by frequency include mismatched solutions (40), outdated
			solutions (39), incorrect solutions (28), and buggy code (1). Fifty-six percent
			of the participants never report the problems back to Stack Overflow.}}%
} \vspace{0.5cm}

@@

Fifty seven participants (66\%) never check for licensing conflicts at all
when reusing Stack Overflow code (see
Figure~\ref{fig:survey_visitor_licensing_conflict_check}). Lastly, 9\% of
the participants experienced legal issues by reusing code snippets on Stack
Overflow (see Figure~\ref{fig:survey_visitor_legal_issue}). We did not
expect that any participant encountered legal issues as we are not
aware of such cases being reported in the literature. It would
be interesting to followup on the kind of legal issues that have been
encountered, however, as we designed the
survey to be anonymous, it was not possible to contact the participants for further details.

@@

\vspace{0.5cm} \noindent\fbox{%
	\parbox[c][1.7cm]{0.98\textwidth}{%
		\textit{For RQ5, 85\% of the participants are not aware of Stack Overflow CC
			BY-SA 3.0 license and 62\% never give attributions to the Stack Overflow posts
			they copied the code snippets from. We found that 66\% of the visitors never check for software
	licensing conflicts between Stack Overflow code snippets and their projects.
	9\% of the participants encountered legal issues.}}%
} \vspace{0.5cm}

\FIXME{Add an overall discussion.}

@@

\subsection{Internal Validity}
We only invited 607
developers to participate in the answerer survey. If all the developers are
invited, which is almost impossible considering 7.6 million users on Stack
Overflow, the results may be different. Nevertheless, we mitigate this threat to
internal validity by selecting the participants based on their Stack Overflow
reputation. This targeted participant selection ensures that we
invite developers who have been actively involved in asking and answering
questions on the site for a long period of time, and refrain from inviting new
users who merely answer a question or two. The highest reputation user invited
to our survey answered 33,933 questions and the lowest reputation user in our
survey answered 116 questions.

@@

From the answerer's responses, we discover that code in Stack Overflow answers
is usually written from scratch to answer a question. Nonetheless, there are
some code snippets that are copied from the answerer's personal or company
projects, or from open source software.
